---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tibble)
```

# Interactive web applications with Shiny for R

This three hour workshop provides the basics of creating interactive web applications in R using Shiny. It consists of three sessions that cover the basics of creating a UI, writing server code with reactive programming and publishing your application.

# Structure

## Session 1: Basics of shiny
* Overview of shiny, summarising its capabilities and use cases.
* Creating a user interface (ui) in R with simple inputs and outputs.
* Writing reactive server code to make a plot using the inputs provided.
* Combine these concepts and make your first shiny app.

## Session 2: Reactive programming
* Understand how shiny server code works with reactive programming.
* Using the building blocks for reactivity: `observe()` changes, `reactive()` objects, using `input$*`, `render*()` output and `isolate()` code.
* The how and why of validating user inputs to safely run code.

## Session 3: Publishing apps
* A brief introduction to the many shiny extension packages available.
* Some quick improvements to the style and appearance of our app using extension packages.
* Discuss options for deploying your app online, including with docker containers and the <shinyapps.io> service

# Schedule

```{r, echo = FALSE}
tribble(
  ~ Time, ~ Activity,
  "09:00 - 09:45", "Session 1 - Basics of shiny",
  "09:45 - 10:00", "Break 1 - Creating your first app",
  "10:00 - 11:00", "Session 2 - Reactive programming",
  "11:00 - 11:15", "Break 2 - Shiny Q & A",
  "11:15 - 12:30", "Session 3 - Publishing apps"
) %>% 
  knitr::kable()
```

# Requirements

Participants are expected to be familiar with writing R code, but no prior experience in website development or shiny is required to get the most out of this workshop. A <shinyapps.io> account is needed to deploy your app to <shinyapps.io> in session 3 (but is not required if you just want to watch this part).

# Related resources

* https://mastering-shiny.org/
* https://github.com/dtkaplan/shinymark
* https://github.com/aimeegott/RStudio-Conf-Intermediate-Shiny
* https://github.com/kellobri/spc-app
* http://teach-shiny.rbind.io/
* https://github.com/grabear/awesome-rshiny
* https://github.com/juliasilge/intro_to_shiny
* https://github.com/laderast/gradual_shiny
* https://github.com/rstudio-education/intro-shiny-rmarkdown
* https://github.com/jcheng5/rstudio2017-shiny-workshop
* https://github.com/rstudio-education/shiny-sdss18
* https://github.com/rstudio-education/shiny-wsds18
* https://github.com/rstudio-education/shiny-jsm18
* https://github.com/mine-cetinkaya-rundel/shiny-training-2017-05-genentech
* https://github.com/goknurginer/R-Ladies-shiny-workshop/
* https://github.com/daattali/advanced-shiny
* [Cheat sheet](https://rstudio.github.io/cheatsheets/shiny.pdf)
